---
title: "Homework 3"
author: "James Livingstone"
date: "10/6/22"
output: html_document
---

```{r setup, include = FALSE}

library(tidyverse)
library(summarytools)

```

You can type text anywhere before, after, or between code chunks. 

# 1. Summary Statistics
```{r homework1}

boilers = read_csv("BOILERS.csv")
boilers %>% 
  select(Man_HRs, Capacity, Pressure) %>%
  descr(stats = "common", transpose = T)

```

# 2. Scatterplots
```{r homework2}

par(mfrow = c(1, 2))
plot(boilers$Capacity, boilers$Man_HRs)
plot(boilers$Pressure, boilers$Man_HRs)

```




Both of these plots look appropriate since they are not non-linear.

# 3. First-Order Multiple Regression Model
```{r homework3}

main_model = lm(Man_HRs ~ Capacity + Pressure, data = boilers)
summary(main_model)

```
# 4. Overall Utility
```{r homework4}


```

F = 36.12, p < 0.001
There is enough evidence to conclude that at least one of Capacity or Pressure 
is significant for predicting man hours.

# 5. Interpret Ra^2
```{r homework5}


```
Ra^2 = 0.6674


66.74% of the variability in the man hours is explained by a linear relationship 
with capacity and pressure. 

# 6. Interactions
```{r homework6}

int_model = lm(Man_HRs ~ Capacity +Pressure + Capacity * Pressure, data = boilers)
summary(int_model)


```
# 7. Interaction Interpretation
```{r homework7}


```

p = 0.03
I would include this interaction of capacity * pressure because it is significant.

# 8. Estimation of Slope


```{r homework8}


#Man_HRs = 3013 + 3.786(250) - 1.529(Pressure) + 0.003439(250)(Pressure)

3013 + 3.786 * 250

```
```{r homework8 part 2}

#Man_HRs = 3595.5 - (1.529 + 0.003439 * 250 (Pressure))
#Man_HRs = 3959.5 - 0.66925(Pressure)

-1.529 + 0.003439 * 250



```


Estimated Change in the man hours for a 1 psi increase in pressure for a boiler drum with a capacity of 250,000 pounds per hour is 3959.5 - 0.66925(Pressure) in which B1 = -0.66925.

# 9. Interpretation of Ra^2
```{r homework9}


```

Ra^2 = 0.7033
70.33% of the variability in the man hours is explained by a linear relationship 
with capacity, pressure, and capacity * pressure.

# 10.Test For Nested Models

```{r homework10}
simple_model = lm(Man_HRs ~ Capacity, data = boilers)
summary(simple_model)
full_model = lm(Man_HRs ~ Capacity +Pressure + Capacity * Pressure, data = boilers)
summary(full_model)
anova(simple_model, full_model, test = "F")


```
F = 2.61, p = 0.089
There is not enough evidence to conclude that there is a significant difference 
between the simple_model(capacity) and the full_model(interaction).

# 11. Which Model Fits the best?
```{r homework11}


```

When investing p value the main_model (first-order multiple regression model with both Capacity and Pressure), this model can be eliminated due to a poor significance in its p value of 0.6561.

Though The full_model (containing the interaction between capacity and pressure) and the simple_model(containing only capacity) both have significant p values of less than 0.001, the full_model is the best fit model.

This full_model (interaction model) has the highest Ra^2 value of 70.33% compared to the simple_model with a lesser 67.52%. 

# 12. Prediction Interval 


```{r homework12}
#PI
predict(full_model, newdata = data.frame(Capacity = 300, Pressure = 750), interval = "prediction", level = 0.95)


```
PI: (715.6349, 6835.692)
We are 95% confident that when the boiler capacity is 300,000 pounds per hour and the pressure is 750psi,the man hours required is between 
715.63 and 6835.69 hours. 