---
title: "Chapter 2 Homework"
author: "James Livingstone"
date: "September 20, 2022"
output: html_document
---

```{r setup, include = FALSE}

library(tidyverse)
library(summarytools)
library(Hmisc)

gasturbine = read.csv('GASTURBINE.csv')




```



# 1.
Table of Summary Statistics

```{r problem 1}

descr(gasturbine, RPM, stats = "common", transpose = T)
descr(gasturbine, CPRATIO, stats = "common", transpose = T)
descr(gasturbine, INLET_TEMP, stats = "common", transpose = T)
descr(gasturbine, EXH_TEMP, stats = "common", transpose = T)
descr(gasturbine, AIRFLOW, stats = "common", transpose = T)
descr(gasturbine, POWER, stats = "common", transpose = T)
descr(gasturbine, HEATRATE, stats = "common", transpose = T)

```

# 2.
Scatterplots
```{r problem 2}




par(mfrow = c(2,3))
plot(gasturbine$RPM, gasturbine$HEATRATE)
plot(gasturbine$CPRATIO, gasturbine$HEATRATE)
plot(gasturbine$INLET_TEMP, gasturbine$HEATRATE)
plot(gasturbine$EXH_TEMP, gasturbine$HEATRATE)
plot(gasturbine$AIRFLOW, gasturbine$HEATRATE)
plot(gasturbine$POWER, gasturbine$HEATRATE)


```




It would not be inappropriate to compute a simple linear regression model for predicting HEATRATE from any of the 
other numerical variables because none of the scatterplots appear to be non-linear
.

# 3.
Three Scatterplots
```{r problem 3}

RPM_model = lm(HEATRATE ~ RPM, data = gasturbine)
summary(RPM_model)
CPRATIO_model = lm(HEATRATE ~ CPRATIO, data = gasturbine)
summary(CPRATIO_model)
INLET_TEMP_model = lm(HEATRATE ~ INLET_TEMP, data = gasturbine)
summary(INLET_TEMP_model)



```
# 4.
Assess the Fit



RPM:
S = 862,
CV = 7.8%,
r= 0.84,
r^2 = 71.2%,
t = 12.69, p-value < 0.001

CPRATIO:
S = 1090,
CV = 9.9%,
r= -0.73,
r^2 = 54.0%,
t = -8.73, p-value < 0.001

INLET_TEMP:
S = 963.1,
CV = 8.7%,
r= -0.8,
r^2 = 64.1%,
t = -10.77, p-value < 0.001

The best model for HEATRATE is RPM vs. HEATRATE model because it has 
comparatively the smallest S value, the lowest CV value, a level of significance
with its p-value being < 0.001, and the highest r^2 value. 

HEATRATE = 9470 + 0.1917(RPM)

If the gasturbine is at 0 RPM, we would expect the HEATRATE to be 9470.
For every 1 RPM increase we would expect a 0.1917 increase in the HEATRATE.

71.2% of the variability in HEATRATE can be explained by a linear relationship
with the level of RPM. 

There is enough evidence to conclude that the amount of RPM has a significant
effect on HEATRATE.


```{r problem 4}

sigma(RPM_model) / mean(gasturbine$HEATRATE) *100 #CV
sigma(CPRATIO_model) / mean(gasturbine$HEATRATE) *100 #CV
sigma(INLET_TEMP_model) / mean(gasturbine$HEATRATE) *100 #CV
gasturbine %>%
  select(RPM, HEATRATE) %>%
  as.matrix() %>%
  rcorr()
gasturbine %>%
  select (CPRATIO, HEATRATE) %>%
  as.matrix() %>%
  rcorr()
gasturbine %>%
  select(INLET_TEMP, HEATRATE) %>%
  as.matrix() %>%
  rcorr()




```
# 5.
Prediction Interval

PI: (8884.723, 12356.26)

We are 95% confident that when the gasturbine has 6000 RPM, the HEATRATE is
between 8884.723 and 12356.26


```{r problem 5}

predict(RPM_model, newdata = data.frame(RPM = 6000), 
        interval = "prediction", level = 0.95)



```
# 6.
Confidence Interval

CI: (10398.76, 10842.22)

We are 95% confident that when the gasturbine has 6000 RPM, the mean HEATRATE is
between 10398.76 and 10842.22

```{r problem 6}

predict(RPM_model, newdata = data.frame(RPM = 6000), 
        interval = "confidence", level = 0.95)




```